Something about Performance, 2D Component of NEMO. (TBC)

### 2016-01-13 nemolite2d_perf.tex
nemolite2d paper: move detailed discussion of roofline model into its own document

>>>>

\subsection{Performance Analysis with the Roofline Model}

Although we have investigated how the performance of the \psykal
version of nemolite2d compares with that or the original, we have not
addressed how efficient the original actually is. In order to do so we
use the Roofline Model~\cite{roofline} which provides a relatively
simple way of characterising the performance of a code in terms of
whether it is memory-bandwidth bound or compute bound. To do so we
follow the approach suggested in~\cite{para_pearls} and use the
well-known STREAM~\cite{stream} and LINPACK~\cite{linpack} benchmarks
in order to get the upper bounds on the memory bandwidth and FLOPS for
the test hardware. Since we are using an Intel Ivybridge CPU we used
the Intel Math Kernel Library implementation of LINPACK.

A key component of the Roofline model is the Arithmetic Intensity of
the code being executed:
\begin{equation}
AI = \frac{\textrm{No. of floating-point operations}}{\textrm{Bytes fetched from memory}}
\end{equation}
We calculated this quantity manually by examining the
source code and counting the number of memory references and
arithmetic operations that it contained. In doing this counting we
assume that any references to adjacent array elements are fetched in a
single cache-line and thus only count once.

\begin{figure}
\centering
\includegraphics[width=\picwidth]{roofline}
\caption{Comparison of the performance achieved by nemolite2d and Shallow}
\label{FIG_roofline}
\end{figure}
